\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-01 paper.tex

We created the gallery out of a horizontal layout group, populated it with
images dynamically in each region, and then had the buttons ``lerp'' the gallery
to different positions in order to switch between each image in a smooth and
pleasing way. As for the audio transcript, we knew we needed a scrollable text
field that could accomodate varying amounts of text, since the audio files
varied so greatly in length. We created a vertical layout group to create a text
field that expanded vertically within predefined bounds to fit an arbitrary
amount of text.

>>>>

We created the gallery out of a horizontal layout group, populated it with
images dynamically in each region, and then had the buttons ``lerp'' the gallery
to different positions in order to switch between each image in a smooth and
pleasing way. As for the audio transcript, we knew we needed a scrollable text
field that could accommodate varying amounts of text, since the audio files
varied so greatly in length. We created a vertical layout group to create a text
field that expanded vertically within predefined bounds to fit an arbitrary
amount of text.
